\chapter{Frequently Asked Questions}

%Each question is will be a \section{}

%\section{I'm a patient. Is there a protected place for me to medicate?}

%Yes! A medical tent is located at the north end of stone village.

\section{I'm hungry! Where is the food?} %make sure this is updated at next core meeting!
 Food is located At:
\begin{itemize}
	\item Munchie Market, 206-218
	\item Northern Bites, 225-228
	\item Ganja Gardens, 219-224
	\item Grubbin' Grove, 200-204
	\item Bud Of Seattle
\end{itemize}

\section{I'm thirsty! Where is the water?}
\begin{itemize}
	\item South Info:Closest water sales booth is located Just behind us.
	\item North Info:Closest water sales booth is located right next to us.
	\item No, I meant free water: H20 station next to ice truck on Blueberry Hill, or the water fountain next to the happy hooker.
\end{itemize}


\section{Where is the smoking going on? Is it legal to smoke at Hempfest?}
Unfortunately, Marijauna is still illegal. Penalties are increased in city parks, as they are considered drug free zones. If you choose to partake as a form of civil disobedience, you do so at your own risk. 

\section{Is Seattle Hempfest the biggest pot rally in the world?}
Yes, as far as we can tell!

\section{Where can I find information about Medical Marijauna?}
Stone Village.

\section{When does Hempfest close?}
Hempfest closes at 8 PM. 

\section{Where can I get official Hempfest swag?}
\begin{itemize}
	\item South Info: 420 Store, Just west of us, between 403 and 404.
	\item North Info: Hempfest General Store, Just south of McWilliams Stage.
\end{itemize}

\section{How do I get a staff tshirt? Can I buy yours?}
Sign up to volunteer at Staff Check in. No, you can only get a shirt if  you volunteer.

\section{Where are the ATMs??}
\begin{itemize}
	\item West side of hemposium
	\item Just around corner from info booth, to the north
	\item Just north of booth 529
	\item North of Ganja Gardens food area
	\item South of Dancesafe, on Hwy 420
\end{itemize}

\section{Is it safe to buy pot brownies at Hempfest?}
No. They are illegal. They are also unpermitted, unregulated food vending and can be dangerous to your health. If you see someone selling brownies, please report to any HF staff with a radio or to HF security. 

\section{Can I have a program?}
Yes. We are asking for a five dollar donation per program. 

\section{Where can I get a beer?}
There is NO alcohol at Hempfest. 

\section{When is the free joint toss?}
What joints? Marijauna is illegal! 

\section{I heard a rumor Snoop Dogg/anyone else not on the schedule is playing, is that true?}
No, all the acts playing are in the schedule.

\section{Where are the closest bathrooms?}
\begin{itemize}
	\item South Info: Directly to the West on Lunday Way.
	\item North Info: Just to the West of us near the bike corral.
\end {itemize}

%\section{What do I do if the police approach me?}
%need to add actual content here, possible to get lit from somewhere? NORML?
 
\section{Can I camp here overnight?}
NO, Camping is illegal in Seattle parks.

\section{Thats some map! How long is the park?}
1.5 miles! 

\section{I need a band aid, I'm having a panic attack, I think I'm dying, where do I go?}
If necessary, escort to booth!
\begin{itemize}
	\item South Info: First aid is located right next to the info booth. 
	\item North Info: Located Just South and West of us, across from Dancesafe.
\end{itemize}











